---
title: "Homework 5"
author: "Ford Holland"
date: "11/2/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(viridis)
library(p8105.datasets)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

## Problem 1

Function to replace missing values in numeric and character vectors.

```{r}
replace_na = function(x) {
  if (!(is.numeric(x) | is.character(x))) {
    stop("This function only supports numeric and character arguments.")
  } else if (is.numeric(x)) {
    x = replace(x, is.na(x), mean(x, na.rm = TRUE)) %>% 
      round(1)
    return(x)
  } else if (is.character(x)) {
    x = replace(x, is.na(x), "virginica")
    return(x)
  }
}
```

Apply this function to the columns of `iris_with_missing` using a `map` statement.

```{r}
iris_imputed = map_df(.x = iris_with_missing, ~replace_na(.x))
```

## Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

* Start with a dataframe containing all file names; the list.files function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r, message=FALSE}
df = tibble(
  file = list.files("data")
) %>% 
  mutate(
    data = map(str_glue("data/{file}"), read_csv) %>% 
      map(pivot_longer, 
          week_1:week_8,
          names_to = "week", 
          values_to = "observation"),
    file = str_replace(file, "\\..*", "")
  ) %>% 
  rename(id = file)
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

It seems the treatment received by the experiment arm caused a noticeable increase in the observations. In fact, the control arm trends downward slightly over time, while the treatment arm displays a stronger, positive trend. 

```{r}
df %>% 
  unnest(cols = data) %>% 
  mutate(
    group = factor(str_detect(id, "con"), 
                   levels = c(TRUE, FALSE),
                   labels = c("control", "experimental")),
    week = str_replace(week, "week_", "")
    ) %>% 
  ggplot(aes(x = week, y = observation, group = id, color = group)) +
  geom_line() +
  labs(title = "Observations over time",
       x = "timepoint (weeks)",
       y = "observation",
       color = "study arm")




# brfss_smart2010 %>% 
#   filter(response == "Excellent") %>% 
#   group_by(location_abbr, year) %>% 
#   mutate(data_value_avg = mean(data_value)) %>% 
#   select(year, location_abbr, data_value_avg) %>% 
#   ungroup() %>% 
#   ggplot(aes(x = year, y = data_value_avg)) +
#   geom_line(aes(group = location_abbr, color = location_abbr)) +
#   theme(legend.position = "none") +
#   labs(title = "Average BRFSS scores over time for all states",
#        x = "Year", 
#        y = "BRFSS score")
```


```{r}

```




```{r}

```




























